Survivable Set Connectivity

### 2015-05-09 draft.tex
made more changes to rackes trees

\begin{definition}
For a given graph $G = (V, E)$, a R\"{a}cke's Tree embedding is a triple of the form $(T,y,\mathrm{map})$ where $T = (V_T,E_T)$ is a rooted tree, $y$ is a capacity function on the edges $E_T$ of $T$, and $\mathrm{map}$ is a function $V_T \cup E_T \to V \cup 2^E$ satisfying the following properties:
\begin{enumerate}
\item For each node $v \in V_T$, $\mathrm{map}(v) \in V$. Thus, the $\mathrm{map}$ function maps nodes in the tree $T$ to nodes in the original graph, $G$.
\item Furthermore, $\mathrm{map}$ restricted to the leaves of $T$ is a bijection with the vertices of $G$. In other words, each leaf of the tree $T$ is in one-to-one correspondence with a vertex of the original graph, $G$.
\item For each edge $e = (u,v) \in E_T$, $\mathrm{map}(e)$ is a set of edges that form a path between $\mathrm{map}(u)$ and $\mathrm{map}(v)$. Note that $\mathrm{map}(u)$ and $\mathrm{map}(v)$ are vertices in $G$, so $\mathrm{map}(e)$ specifies a set of edges in $G$.
%\item For some edge $e \in E_T$, $y_e$ (the cost of the edge) is a special quantity. Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$. Figure~\ref{fig:rackecut} gives an example for one such cut induced by an edge.
\begin{align}
y_e &= \sum_{e' \in \delta(S)} x_e
\end{align}
\end{enumerate}
\end{definition}

To summarize, the $\mathrm{map}$ function sends vertices in $V_T$ to vertices in $V$, and sends edges in $T$ to paths in $G$. With these definitions, we can consider the inverse function $\mathrm{map}^{-1}$. Note that multiple vertices in $T$ could map to the same vertex in $V$, so we must specify that for $v \in G$, the value of $\mathrm{map}^{-1}(v)$ is the unique \emph{leaf} vertex in $V_T$ that maps to $v$. We will also consider $\mathrm{map}^{-1}$ applied to sets of vertices $W \subseteq V$, and define it in the obvious way: $\mathrm{map}^{-1}(W) = \bigcup_{v \in W} \mathrm{map}^{-1}(v)$.

@@

Having made these definition, we can refer to the inverse $\text{map}^{-1}$ in the obvious manner. $\text{map}^{-1}$ on a vertex will map to the corresponding leaf, and $\text{map}^{-1}$ on an edge in the graph will map to all edges in the tree whose paths contain that edge.

>>>>

\begin{definition}
For a given graph $G = (V, E)$, a R\"{a}cke's Tree embedding is a triple of the form $(T,y,\mathrm{map})$ where $T = (V_T,E_T)$ is a rooted tree, $y$ is a capacity function on the edges $E_T$ of $T$, and $\mathrm{map}$ is a function $V_T \cup E_T \to V \cup 2^E$ satisfying the following properties:
\begin{enumerate}
\item For each node $v \in V_T$, $\mathrm{map}(v) \in V$. Thus, the $\mathrm{map}$ function maps nodes in the tree $T$ to nodes in the original graph, $G$.
\item Furthermore, $\mathrm{map}$ restricted to the leaves of $T$ is a bijection with the vertices of $G$. In other words, each leaf of the tree $T$ is in one-to-one correspondence with a vertex of the original graph, $G$.
\item For each edge $e = (u,v) \in E_T$, $\mathrm{map}(e)$ is a set of edges that form a path between $\mathrm{map}(u)$ and $\mathrm{map}(v)$. Note that $\mathrm{map}(u)$ and $\mathrm{map}(v)$ are vertices in $G$, so $\mathrm{map}(e)$ specifies a set of edges in $G$.
%\item For some edge $e \in E_T$, $y_e$ (the cost of the edge) is a special quantity. Removing $y_e$ cuts the tree into two components, and so the leaves in the two components form a cut $\delta(S)$. Figure~\ref{fig:rackecut} gives an example for one such cut induced by an edge.
%\begin{align}
%y_e &= \sum_{e' \in \delta(S)} x_e
%\end{align}
\end{enumerate}
\end{definition}

With this setup, we can try to define the inverse function, $\mathrm{map}^{-1}$. If we try to compute $\mathrm{map}^{-1}(v)$ for some $v \in V$, we note that multiple vertices in $T$ could map to $v$. Thus, we specify that $\mathrm{map}^{-1}(v)$ be the unique \emph{leaf} vertex in $V_T$ that maps to $v$. We will also consider $\mathrm{map}^{-1}$ applied to sets of vertices $W \subseteq V$, and we define it in the obvious way: $\mathrm{map}^{-1}(W) = \bigcup_{v \in W} \mathrm{map}^{-1}(v)$.

For edges $e = (u,v) \in E$, we define $\mathrm{map}^{-1}(e) = \{ f \in E_T | e \in \mathrm{map}(f)\}$. This is simply the set of all edges $f$ in the tree $T$ that get mapped to a set of edges $\mathrm{map}(f)$ that contain $e$. Again, this defintiion can be extended to sets of edges $F \subseteq E$, so that $\mathrm{map}^{-1}(F) = \bigcup_{e \in F} \mathrm{map}^{-1}(e)$.

@@
